Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-07-10 analysis/memo2_TAS_reviewers.Rmd
minor edit to memo

We appreciate this suggestion, but we worry that making this point here in terms of Type I and Type II error might lead to net confusion. The statement that "errors of Type I are okay" is fine if it refers to the idea that at step two of the _Batson_ sequence (whether to find a _prima facie_ case), one should tolerate more false positives (false inferences of illegal strike bias, because all it does is lead the judge to force the striking attorney to offer up reasons for the strikes and then have the judge assess the credibility of those reasons along with the other evidence. Such errors, however, are far less tolerable -- not as okay -- at step four, where the judge has to consider historical strike data along with all the other evidence and ultimately find whether illegal strike bias is more likely than not. And such errors are worse still as the judge assigns more relative weight to the inference from historical strike data as compared to other items of evidence.

>>>>

We appreciate this suggestion, but we worry that making this point here in terms of Type I and Type II error might lead to net confusion. The statement that "errors of Type I are okay" is fine if it refers to the idea that at step two of the _Batson_ sequence (whether to find a _prima facie_ case), one should tolerate more false positives (false inferences of illegal strike bias), because all it does is lead the judge to force the striking attorney to offer up reasons for the strikes and then have the judge assess the credibility of those reasons along with the other evidence. Such errors, however, are far less tolerable -- not as okay -- at step four, where the judge has to consider historical strike data along with all the other evidence and ultimately find whether illegal strike bias is more likely than not. And such errors are worse still as the judge assigns more relative weight to the inference from historical strike data as compared to other items of evidence.
